Hierarchical Time Series Forecasting in Emergency Medical Services

### 2023-12-14 manuscript/main.tex
finalised comments of AE

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{todonotes,mathtools,bm,amsmath,mathpazo}
\mathtoolsset{showonlyrefs}
\setlength{\parindent}{0cm}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\journal{Journal of Service Research}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-harv}
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Hierarchical Time Series Forecasting in Emergency Medical Services},
  pdfkeywords={healthcare, emergency services, forecast
reconciliation, ambulance demand, regression},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{keyword}
    healthcare \sep emergency services \sep forecast
reconciliation \sep ambulance demand \sep 
    regression
\end{keyword}
\end{frontmatter}
    \section{Introduction}\label{sec-intro}

@@

\section{Research background}\label{sec-lit}

@@

\begin{table}

\caption{\label{tbl-literature}Summary of some studies on forecasting in
Emergency Medical Services}

\centering{

@@

\resizebox{\linewidth}{!}{
\begin{tabular}{lr>{\raggedright\arraybackslash}p{6em}>{\raggedright\arraybackslash}p{4em}>{\raggedright\arraybackslash}p{10em}>{\raggedright\arraybackslash}p{8em}ll}
\toprule
Reference & Year & Variable & Horizon & Method & Metric & Probabilistic & Reconciliation\\
\midrule
Current study & 2023 & Ambulance demand & 84 days & Stationary,  Exponential Smoothing State Space (ETS), Poisson regression using Generalized Linear Model (GLM) and tscount (TSGLM), a simple empirical distribution and an ensemble method & MASE, MSSE, CRPS & YES & YES\\
Al-Azzani et al. & 2021 & Call volume & 7 , 30 ,  90 days & ARIMA, Holt Winters, Multiple Regression, and Singular Spectrum Analysis & RMSE, MAPE & NO & NO\\
Haugsbø et al. & 2021 & Ambulance demand in Spatio-temporal & 1hour & MLP, LSTM & MAE, MSE, Cross-Entropy & YES & NO\\
Grekousis et al. & 2019 & Locations of incidents & 1 hour & MLP and Hungarian algorithm & RMSE & NO & NO\\
Ibrahim et al. & 2016 & Call volume & 1, 7 , 14 days & multiplicative univariate forecasting, univariate mixed-effects, bivariate mixed-effects model, and bivariate mixed-effects & RMSE, prediction interval coverage & Partial & NO\\
Vile et al. & 2012 & Ambulance demand & 7, 14, 21,  28 day & Singular Spectrum Analysis, ARIMA,  Holt-Winters & RMSE & NO & NO\\
Sasaki et al. & 2010 & Ambulance demand & 5 years & OLS regression & R\textasciicircum{}2 & NO & NO\\
\bottomrule
\end{tabular}}
\endgroup{}

\end{table}%

\section{Experiment setup}\label{sec-experiment}

@@

\subsection{Data}\label{sec-data}

@@

\centering{

\includegraphics[width=0.6\textwidth,height=\textheight]{main_files/figure-pdf/fig-hierarchy-1.pdf}

@@

\subcaption{\label{fig-hierarchy-1}Hierarchical structure: Attended
incidents in the whole country are disaggregated into 3 control areas
and then into 7 different healthboards.}

\end{minipage}%
%
\begin{minipage}[t]{0.02\linewidth}
~\end{minipage}%
%
\begin{minipage}[t]{0.42\linewidth}

\centering{

\includegraphics[width=0.6\textwidth,height=\textheight]{../img/group.png}

@@

\subcaption{\label{fig-hierarchy-2}Grouped structure: Incidents could be
grouped into priority (i.e.~Red, Amber \& Green) and the nature of
attended incident (i.e.~there are 35 different nature of incidents
including chest pain, breathing problems, heart attack, stroke, and so
on). The symbol * refers to the crossed attributes between hierarchical
and grouped levels.}

\end{minipage}%

@@

\end{figure}%

@@

\begin{table}

\caption{\label{tbl-hierarchy}Number of time series in each level for
the hierarchical \& grouped structure of attended incidents}

\centering{

\centering
\begin{threeparttable}
\begin{tabular}{lr}
\toprule
Level & Number of series\\
\midrule
All country & 1\\
Control & 3\\
Health board & 7\\
Priority & 3\\
Priority * Control & 9\\
\addlinespace
Priority * Health board & 21\\
Nature of incident & 35\\
Nature of incident * Control & 105\\
Nature of incident * Health board & 245\\
Priority * Nature of incident & 104\\
\addlinespace
Control * Priority * Nature of incident & 306\\
Control * Health board * Priority * Nature of incident (Bottom level) & 691\\
Total & 1530\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item \textit{Note: } 
\item Due to certain combinations of the nature of incident with other variables, there is a lack of representation in the dataset. As a result, for example, instead of the calculation 3 * 35 = 105, it would be modified to 3 * 35-1 = 104.
\end{tablenotes}
\end{threeparttable}

\end{table}%

@@

\centering{

\includegraphics[width=0.7\textwidth,height=\textheight]{main_files/figure-pdf/fig-feature-1.pdf}

@@

\centering{

\includegraphics[width=1\textwidth,height=\textheight]{main_files/figure-pdf/fig-dataviz2-1.pdf}

@@

\subsection{Forecasting methods}\label{forecasting-methods}

@@

\subsection{Performance evaluation}\label{performance-evaluation}

@@

A related measure is MSSE
\citep{hyndman2021forecasting, makridakis2022m5}, which uses squared
errors rather than absolute errors:
\begin{equation}\phantomsection\label{eq-RMSSE}{
  \text{MSSE} = \text{mean}(q_{j}^2),
}\end{equation} where, \[
  q^2_{j} = \frac{ e^2_{j}}
 {\displaystyle\frac{1}{T-m}\sum_{t=m+1}^T (y_{t}-y_{t-m})^2},
\] Again, this is scale-independent, and smaller MSSE values suggest
more accurate forecasts.

@@

To measure the forecast distribution accuracy, we calculate the
Continuous Rank Probability Score
\citep{gneiting2014probabilistic, hyndman2021forecasting}. It rewards
sharpness and penalizes miscalibration, so it measures overall
performance of the forecast distribution.
\begin{equation}\phantomsection\label{eq-CRPS}{
  \text{CRPS} = \text{mean}(p_j),
}\end{equation} where \[
  p_j = \int_{-\infty}^{\infty} \left(G_j(x) - F_j(x)\right)^2dx,
\] where \(G_j(x)\) is the forecasted probability distribution function
for forecast horizon \(j\), and \(F_j(x)\) is the true probability
distribution function for the same period.

@@

\section{Hierarchical and grouped time series forecasting
techniques}\label{sec-htc}

@@

\subsection{Independent (base
forecast)}\label{independent-base-forecast}

@@

\subsection{Reconciliation methods}\label{reconciliation-methods}

@@

\subsubsection{Notations}\label{notations}

@@

\subsubsection{Bottom-up (BU) and linear reconciliation
methods}\label{bottom-up-bu-and-linear-reconciliation-methods}

@@

\section{Results and discussion}\label{sec-results}

@@

\begin{table}

\caption{\label{tbl-result}Average forecast performance calculated on
the test sets at forecast horizons \(h=43,\dots,84\) days, with time
series cross validation applied to attended incident data. The test set
consists of 462 days. The best approach is highlighted in bold. Point
forecast accuracy is measured using MASE and MSSE, while probabilistic
forecast accuracy is measured using CRPS.}

\centering{

\begin{tabular}{llrrrr}
\toprule
Method & Model & Total & Control areas & Health boards & Bottom\\
\midrule
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{MSSE}}\\
\hspace{1em}Base & Stationary & 1.139 & 1.059 & 1.047 & 1.019\\
\hspace{1em}Base & ETS & 0.963 & 0.930 & 0.899 & 1.038\\
\hspace{1em}Base & GLM & 0.910 & 0.940 & 0.923 & \textbf{1.002}\\
\hspace{1em}Base & TSGLM & 0.911 & 0.939 & 0.924 & 1.005\\
\hspace{1em}Base & Ensemble & 0.782 & 0.856 & 0.876 & 1.008\\
\hspace{1em}MinT & Stationary & 1.138 & 1.059 & 1.047 & 2.651\\
\hspace{1em}MinT & ETS & 0.877 & 0.916 & 0.915 & 1.289\\
\hspace{1em}MinT & GLM & 0.848 & 0.901 & 0.902 & 2.493\\
\hspace{1em}MinT & TSGLM & 0.852 & 0.903 & 0.903 & 2.513\\
\hspace{1em}MinT & Ensemble & \textbf{0.753} & \textbf{0.844} & \textbf{0.872} & 2.260\\
\addlinespace[0.3em]
\hline
\multicolumn{6}{l}{\textbf{MASE}}\\
\hspace{1em}Base & Stationary & 1.169 & 1.056 & 1.062 & 1.031\\
\hspace{1em}Base & ETS & 0.979 & 0.875 & 0.816 & \textbf{0.975}\\
\hspace{1em}Base & GLM & 0.813 & 0.897 & 0.875 & 1.009\\
\hspace{1em}Base & TSGLM & 0.822 & 0.901 & 0.875 & 1.050\\
\hspace{1em}Base & Ensemble & 0.599 & 0.729 & 0.774 & 0.993\\
\hspace{1em}MinT & Stationary & 1.168 & 1.057 & 1.062 & 2.095\\
\hspace{1em}MinT & ETS & 0.785 & 0.852 & 0.845 & 0.994\\
\hspace{1em}MinT & GLM & 0.720 & 0.827 & 0.837 & 1.803\\
\hspace{1em}MinT & TSGLM & 0.722 & 0.833 & 0.839 & 1.851\\
\hspace{1em}MinT & Ensemble & \textbf{0.560} & \textbf{0.706} & \textbf{0.765} & 1.557\\
\addlinespace[0.3em]
\hline
\multicolumn{6}{l}{\textbf{CRPS}}\\
\hspace{1em}Base & Stationary & 30.387 & 10.882 & 5.500 & 0.302\\
\hspace{1em}Base & ETS & 14.309 & 6.074 & 3.476 & 0.244\\
\hspace{1em}Base & GLM & 15.396 & 6.253 & 3.576 & 0.244\\
\hspace{1em}Base & TSGLM & 15.316 & 6.227 & 3.575 & 0.245\\
\hspace{1em}Base & Ensemble & 12.978 & \textbf{5.727} & 3.430 & 0.243\\
\hspace{1em}MinT & Stationary & 30.368 & 10.902 & 5.498 & 0.313\\
\hspace{1em}MinT & ETS & 13.515 & 5.967 & 3.547 & \textbf{0.243}\\
\hspace{1em}MinT & GLM & 13.839 & 5.917 & 3.453 & 0.246\\
\hspace{1em}MinT & TSGLM & 14.000 & 5.947 & 3.455 & 0.248\\
\hspace{1em}MinT & Ensemble & \textbf{12.585} & 5.728 & \textbf{3.426} & 0.247\\
\bottomrule
\end{tabular}

\end{table}%

@@

\centering{

\includegraphics[width=1\textwidth,height=\textheight]{main_files/figure-pdf/fig-accuracy-1.pdf}

@@

\subsection{An illustration of probabilistic forecast for EMS
demand}\label{an-illustration-of-probabilistic-forecast-for-ems-demand}

@@

\centering{

\includegraphics[width=1\textwidth,height=\textheight]{main_files/figure-pdf/fig-forecast-density-1.pdf}

@@

\end{figure}%

\section{Conclusion}\label{sec-conclusion}

@@

\section*{Reproducibility}\label{reproducibility}
\addcontentsline{toc}{section}{Reproducibility}

>>>>

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{todonotes,mathtools,bm,amsmath,mathpazo}
\mathtoolsset{showonlyrefs}
\setlength{\parindent}{0cm}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\journal{Journal of Service Research}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-harv}
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Hierarchical Time Series Forecasting in Emergency Medical Services},
  pdfkeywords={healthcare, emergency services, forecast
reconciliation, ambulance demand, regression},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{keyword}
    healthcare \sep emergency services \sep forecast
reconciliation \sep ambulance demand \sep 
    regression
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, interior hidden, borderline west={3pt}{0pt}{shadecolor}, breakable, sharp corners, enhanced, frame hidden]}{\end{tcolorbox}}\fi

\hypertarget{sec-intro}{%
\section{Introduction}\label{sec-intro}}

@@

\hypertarget{sec-lit}{%
\section{Research background}\label{sec-lit}}

@@

\hypertarget{tbl-literature}{}
\begin{landscape}\begin{table}
\caption{\label{tbl-literature}Summary of some studies on forecasting in Emergency Medical Services }\tabularnewline

@@

\resizebox{\linewidth}{!}{
\begin{tabular}{lr>{\raggedright\arraybackslash}p{6em}>{\raggedright\arraybackslash}p{4em}>{\raggedright\arraybackslash}p{10em}>{\raggedright\arraybackslash}p{8em}lll}
\toprule
Reference & Year & Variable & Horizon & Method & Metric & Probabilistic & Reconciliation & Reproducibility\\
\midrule
Current study & 2023 & Ambulance demand & 84 days & Stationary,  Exponential Smoothing State Space (ETS), Poisson regression using Generalized Linear Model (GLM) and tscount (TSGLM), a simple empirical distribution and an ensemble method & MASE, MSSE, CRPS & YES & YES & YES\\
Al-Azzani et al. & 2021 & Call volume & 7 , 30 ,  90 days & ARIMA, Holt Winters, Multiple Regression, and Singular Spectrum Analysis & RMSE, MAPE & NO & NO & No\\
Haugsbø et al. & 2021 & Ambulance demand in Spatio-temporal & 1hour & MLP, LSTM & MAE, MSE, Cross-Entropy & YES & NO & No\\
Grekousis et al. & 2019 & Locations of incidents & 1 hour & MLP and Hungarian algorithm & RMSE & NO & NO & No\\
Ibrahim et al. & 2016 & Call volume & 1, 7 , 14 days & multiplicative univariate forecasting, univariate mixed-effects, bivariate mixed-effects model, and bivariate mixed-effects & RMSE, prediction interval coverage & Partial & NO & No\\
Vile et al. & 2012 & Ambulance demand & 7, 14, 21,  28 day & Singular Spectrum Analysis, ARIMA,  Holt-Winters & RMSE & NO & NO & No\\
Sasaki et al. & 2010 & Ambulance demand & 5 years & OLS regression & R\textasciicircum{}2 & NO & NO & No\\
\bottomrule
\end{tabular}}
\endgroup{}
\end{table}
\end{landscape}

\hypertarget{sec-experiment}{%
\section{Experiment setup}\label{sec-experiment}}

@@

\hypertarget{sec-data}{%
\subsection{Data}\label{sec-data}}

@@

{\centering

\raisebox{-\height}{

\includegraphics{main_files/figure-pdf/fig-hierarchy-1.pdf}

@@

@@

\subcaption{\label{fig-hierarchy-1}Hierarchical structure: Attended
incidents in the whole country are disaggregated into 3 control areas
and then into 7 different healthboards.}
\end{minipage}%
%
\begin{minipage}[t]{0.02\linewidth}

{\centering

~

\end{minipage}%
%
\begin{minipage}[t]{0.42\linewidth}

{\centering

\raisebox{-\height}{

\includegraphics{../img/group.png}

\subcaption{\label{fig-hierarchy-2}Grouped structure: Incidents could be
grouped into priority (i.e.~Red, Amber \& Green) and the nature of
attended incident (i.e.~there are 35 different nature of incidents
including chest pain, breathing problems, heart attack, stroke, and so
on). The symbol * refers to the crossed attributes between hierarchical
and grouped levels.}
\end{minipage}%

@@

\end{figure}

@@

\hypertarget{tbl-hierarchy}{}
\begin{table}
\caption{\label{tbl-hierarchy}Number of time series in each level for the hierarchical \& grouped
structure of attended incidents }\tabularnewline

\centering
\begin{threeparttable}
\begin{tabular}{lr}
\toprule
Level & Number of series\\
\midrule
All country & 1\\
Control & 3\\
Health board & 7\\
Priority & 3\\
Priority * Control & 9\\
\addlinespace
Priority * Health board & 21\\
Nature of incident & 35\\
Nature of incident * Control & 105\\
Nature of incident * Health board & 245\\
Priority * Nature of incident & 104\\
\addlinespace
Control * Priority * Nature of incident & 306\\
Control * Health board * Priority * Nature of incident (Bottom level) & 691\\
Total & 1530\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item \textit{Note: } 
\item Due to certain combinations of the nature of incident with other variables, there is a lack of representation in the dataset. As a result, for example, instead of the calculation 3 * 35 = 105, it would be modified to 3 * 35-1 = 104.
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

{\centering \includegraphics[width=0.7\textwidth,height=\textheight]{main_files/figure-pdf/fig-feature-1.pdf}

@@

{\centering \includegraphics[width=1\textwidth,height=\textheight]{main_files/figure-pdf/fig-dataviz2-1.pdf}

@@

\hypertarget{forecasting-methods}{%
\subsection{Forecasting methods}\label{forecasting-methods}}

@@

\hypertarget{performance-evaluation}{%
\subsection{Performance evaluation}\label{performance-evaluation}}

@@

A related measure is MSSE
\citep{hyndman2021forecasting, makridakis2022m5}, which uses squared
errors rather than absolute errors:
\begin{equation}\protect\hypertarget{eq-RMSSE}{}{
  \text{MSSE} = \text{mean}(q_{j}^2),
}\label{eq-RMSSE}\end{equation} where, \[
  q^2_{j} = \frac{ e^2_{j}}
 {\displaystyle\frac{1}{T-m}\sum_{t=m+1}^T (y_{t}-y_{t-m})^2},
\] Again, this is scale-independent, and smaller MSSE values suggest
more accurate forecasts.

@@

To measure the forecast distribution accuracy, we calculate the
Continuous Rank Probability Score
\citep{gneiting2014probabilistic, hyndman2021forecasting}. It rewards
sharpness and penalizes miscalibration, so it measures overall
performance of the forecast distribution.
\begin{equation}\protect\hypertarget{eq-CRPS}{}{
  \text{CRPS} = \text{mean}(p_j),
}\label{eq-CRPS}\end{equation} where \[
  p_j = \int_{-\infty}^{\infty} \left(G_j(x) - F_j(x)\right)^2dx,
\] where \(G_j(x)\) is the forecasted probability distribution function
for forecast horizon \(j\), and \(F_j(x)\) is the true probability
distribution function for the same period.

@@

\hypertarget{sec-htc}{%
\section{Hierarchical and grouped time series forecasting
techniques}\label{sec-htc}}

@@

\hypertarget{independent-base-forecast}{%
\subsection{Independent (base
forecast)}\label{independent-base-forecast}}

@@

\hypertarget{reconciliation-methods}{%
\subsection{Reconciliation methods}\label{reconciliation-methods}}

@@

\hypertarget{notations}{%
\subsubsection{Notations}\label{notations}}

@@

\hypertarget{bottom-up-bu-and-linear-reconciliation-methods}{%
\subsubsection{Bottom-up (BU) and linear reconciliation
methods}\label{bottom-up-bu-and-linear-reconciliation-methods}}

@@

\hypertarget{sec-results}{%
\section{Results and discussion}\label{sec-results}}

@@

\hypertarget{tbl-result}{}
\begin{table}
\caption{\label{tbl-result}Average forecast performance calculated on the test sets at forecast
horizons \(h=43,\dots,84\) days, with time series cross validation
applied to attended incident data. The test set consists of 462 days.
The best approach is highlighted in bold. Point forecast accuracy is
measured using MASE and MSSE, while probabilistic forecast accuracy is
measured using CRPS. }\tabularnewline

\centering
\begin{tabular}{llrrrr}
\toprule
Method & Model & Total & Control areas & Health boards & Bottom\\
\midrule
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{MSSE}}\\
\hspace{1em}Base & Stationary & 1.139 & 1.059 & 1.047 & 1.019\\
\hspace{1em}Base & ETS & 0.963 & 0.930 & 0.899 & 1.038\\
\hspace{1em}Base & GLM & 0.910 & 0.940 & 0.923 & \textbf{1.002}\\
\hspace{1em}Base & TSGLM & 0.911 & 0.939 & 0.924 & 1.005\\
\hspace{1em}Base & Ensemble & 0.782 & 0.856 & 0.876 & 1.008\\
\hspace{1em}MinT & Stationary & 1.138 & 1.059 & 1.047 & 2.651\\
\hspace{1em}MinT & ETS & 0.877 & 0.916 & 0.915 & 1.289\\
\hspace{1em}MinT & GLM & 0.848 & 0.901 & 0.902 & 2.493\\
\hspace{1em}MinT & TSGLM & 0.852 & 0.903 & 0.903 & 2.513\\
\hspace{1em}MinT & Ensemble & \textbf{0.753} & \textbf{0.844} & \textbf{0.872} & 2.260\\
\addlinespace[0.3em]
\hline
\multicolumn{6}{l}{\textbf{MASE}}\\
\hspace{1em}Base & Stationary & 1.169 & 1.056 & 1.062 & 1.031\\
\hspace{1em}Base & ETS & 0.979 & 0.875 & 0.816 & \textbf{0.975}\\
\hspace{1em}Base & GLM & 0.813 & 0.897 & 0.875 & 1.009\\
\hspace{1em}Base & TSGLM & 0.822 & 0.901 & 0.875 & 1.050\\
\hspace{1em}Base & Ensemble & 0.599 & 0.729 & 0.774 & 0.993\\
\hspace{1em}MinT & Stationary & 1.168 & 1.057 & 1.062 & 2.095\\
\hspace{1em}MinT & ETS & 0.785 & 0.852 & 0.845 & 0.994\\
\hspace{1em}MinT & GLM & 0.720 & 0.827 & 0.837 & 1.803\\
\hspace{1em}MinT & TSGLM & 0.722 & 0.833 & 0.839 & 1.851\\
\hspace{1em}MinT & Ensemble & \textbf{0.560} & \textbf{0.706} & \textbf{0.765} & 1.557\\
\addlinespace[0.3em]
\hline
\multicolumn{6}{l}{\textbf{CRPS}}\\
\hspace{1em}Base & Stationary & 30.387 & 10.882 & 5.500 & 0.302\\
\hspace{1em}Base & ETS & 14.309 & 6.074 & 3.476 & 0.244\\
\hspace{1em}Base & GLM & 15.396 & 6.253 & 3.576 & 0.244\\
\hspace{1em}Base & TSGLM & 15.316 & 6.227 & 3.575 & 0.245\\
\hspace{1em}Base & Ensemble & 12.978 & \textbf{5.727} & 3.430 & 0.243\\
\hspace{1em}MinT & Stationary & 30.368 & 10.902 & 5.498 & 0.313\\
\hspace{1em}MinT & ETS & 13.515 & 5.967 & 3.547 & \textbf{0.243}\\
\hspace{1em}MinT & GLM & 13.839 & 5.917 & 3.453 & 0.246\\
\hspace{1em}MinT & TSGLM & 14.000 & 5.947 & 3.455 & 0.248\\
\hspace{1em}MinT & Ensemble & \textbf{12.585} & 5.728 & \textbf{3.426} & 0.247\\
\bottomrule
\end{tabular}
\end{table}

@@

{\centering \includegraphics[width=1\textwidth,height=\textheight]{main_files/figure-pdf/fig-accuracy-1.pdf}

@@

\hypertarget{an-illustration-of-probabilistic-forecast-for-ems-demand}{%
\subsection{An illustration of probabilistic forecast for EMS
demand}\label{an-illustration-of-probabilistic-forecast-for-ems-demand}}

@@

{\centering \includegraphics[width=1\textwidth,height=\textheight]{main_files/figure-pdf/fig-forecast-density-1.pdf}

@@

\end{figure}

\hypertarget{sec-conclusion}{%
\section{Conclusion}\label{sec-conclusion}}

@@

\hypertarget{reproducibility}{%
\section*{Reproducibility}\label{reproducibility}}
\addcontentsline{toc}{section}{Reproducibility}
